Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs

### 2020-08-03 FDT2020/Introduction.tex
Carr-Vempala point figure added, TSP book reference added, Comments replied

There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP) or 2EC.
\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

Consider a graph $G=(V,E)$. A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$.
\cindy{Every pair of vertices on the cycle is connected this way? It sounds like that, though I don't recall that being necessary. We probably have a figure from an old version we could include if it's not too much trouble.  This will help reviewers and future readers understand much more easily, especially that there could be far more than 12 vertices in the overall solution.}
Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point. We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
\cindy{This sounds like a contribution of the paper.}
Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.

>>>>

There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP) or 2EC (see \cite{tspbook})
\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

Consider a graph $G=(V,E)$. A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint})
\cindy{Every pair of vertices on the cycle is connected this way? It sounds like that, though I don't recall that being necessary. We probably have a figure from an old version we could include if it's not too much trouble.  This will help reviewers and future readers understand much more easily, especially that there could be far more than 12 vertices in the overall solution.}

\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?}

\begin{figure}
\centering
\begin{tikzpicture}[scale=0.4]

\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};

\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};

\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);

\node (1) at (0,4) {{1}};
\node (2) at (2.83,2.83) {{2}};
\node (3) at (4,0) {{3}};
\node (4) at (2.83,-2.83) {{4}};
\node (5) at (0,-4) {{5}};
\node (6) at (-2.83,-2.83) {{6}};
\node (7) at (-4,0) {{7}};
\node (8) at (-2.83,2.83) {{8}};
\end{tikzpicture}
\caption{A Carr-Vempala point with 8 vertices on its cycle. Dashed edges represent paths where each edge on the path have $x_e =1$.}
\label{fig:CVpoint}
\end{figure}

Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point. We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
